An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data

### 2015-03-16 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
presenters

\textbf{Thomas Bosch} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
His research topic is all about RDF validation.
More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).

>>>>

\textbf{Thomas Bosch} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student in Computer Science.
His research topic is all about RDF validation.
He investigates how to validate any RDF constraints (formulated by arbitrary constraint languages) and how to express them generically. 
He presented his work at international conferences and workshops (e.g. WWW, ISWC, DC, and Dagstuhl seminars). 
Thomas Bosch is member of the RDF Vocabularies Working Group\footnote{\url{http://www.ddialliance.org/alliance/working-groups#RDF}} of the DDI Alliance,
part of the editorial board of the  DCMI RDF Application Profiles Task Group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}, 
editor of the specifications DDI-RDF Discovery Vocabulary (Disco)\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}
and Physical Data Description (PHDD)\footnote{A vocabulary to represent data in a rectangular format in RDF; \url{https://github.com/linked-statistics/physical-data-description}},
and contributes to the W3C RDF Data Shapes Working Group\footnote{\url{http://www.w3.org/2014/data-shapes/charter}}.

### 2015-03-16 paper/paper7/paper7-appendix.tex
presenters

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}}
	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}). 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures. 
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-01:}}
	Dimensions have range (\emph{IC-4} \cite{CyganiakReynolds2014}) - 
	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
	Concept dimensions have code lists (\emph{IC-5} \cite{CyganiakReynolds2014}) - 
	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04:}}
	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-05:}}
	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-06:}}
	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}). 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01:}}
	Codes from code list (\emph{IC-19} \cite{CyganiakReynolds2014}) - 
	If a dimension property has a \emph{qb:codeList}, then the value of the dimension property on every \emph{qb:Observation} must be in the code list. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-VALUE-IS-VALID-FOR-DATATYPE-01:}}
	Datatype consistency (\emph{IC-0} \cite{CyganiakReynolds2014}) -  
	The RDF graph must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph. 
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-01:}}
	Codes from hierarchy (\emph{IC-20} \cite{CyganiakReynolds2014}) -  
	If a dimension property has a \emph{qb:HierarchicalCodeList} with a non-blank \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the \emph{qb:parentChildProperty} links. 
	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-02:}}
	Codes from hierarchy (inverse) (\emph{IC-21} \cite{CyganiakReynolds2014}) -  
	If a dimension property has a \emph{qb:HierarchicalCodeList} with an inverse \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the inverse \emph{qb:parentChildProperty} links. 
\end{itemize}

>>>>

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
	\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}} 
	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
	\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}). 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-10:}}
	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-11:}}
	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
	\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-01:}}
	Dimensions have range (\emph{IC-4} \cite{CyganiakReynolds2014}) - 
	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
	Concept dimensions have code lists (\emph{IC-5} \cite{CyganiakReynolds2014}) - 
	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}}
	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04	:}}
	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}). 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01:}}
	Codes from code list (\emph{IC-19} \cite{CyganiakReynolds2014}) - 
	If a dimension property has a \emph{qb:codeList}, then the value of the dimension property on every \emph{qb:Observation} must be in the code list. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-VALUE-IS-VALID-FOR-DATATYPE-01:}}
	Datatype consistency (\emph{IC-0} \cite{CyganiakReynolds2014}) -  
	The RDF graph must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-01:}}
	Codes from hierarchy (\emph{IC-20} \cite{CyganiakReynolds2014}) -  
	If a dimension property has a \emph{qb:HierarchicalCodeList} with a non-blank \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the \emph{qb:parentChildProperty} links. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-02:}}
	Codes from hierarchy (inverse) (\emph{IC-21} \cite{CyganiakReynolds2014}) -  
	If a dimension property has a \emph{qb:HierarchicalCodeList} with an inverse \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the inverse \emph{qb:parentChildProperty} links. 
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

### 2015-03-16 paper/paper7/paper7-evaluation.tex
presenters

\begin{itemize}
	\item DwB Resource Discovery Portal
	\begin{itemize}
	  \item Metadata records for each study are available on the study landing pages.
		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
	\end{itemize}
\end{itemize}

@@

>>>>

\begin{itemize}
  \item Microdata Information System (Missy)
	\item DwB Resource Discovery Portal
	\begin{itemize}
	  \item Metadata records for each study are available on the study landing pages.
		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
	\end{itemize}
	\item DDA and SND SPARQL endpoint\footnote{\url{http://ddi-rdf.borsna.se/}} 
	\begin{itemize}
		\item triples: 2,271,415
		\item studies: 1,490
		\item universes: 10,188
		\item questions: 139,237
		\item variables: 80,070
	\end{itemize}
\end{itemize}

@@

\section{XKOS}

\begin{itemize}
	\item Nomenclature d'activités française (NAF)\footnote{\url{http://rdf.insee.fr/codes/index.html}}: French classification expressed in XKOS. the French refinement of the NACE, because it has explanatory notes.
	\item Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)\footnote{\url{http://rdf.insee.fr/codes/index.html}}: French classification expressed in XKOS.
	\item Nomenclature des catégories juridiques (CJ)\footnote{\url{http://rdf.insee.fr/codes/index.html}}: French classification expressed in XKOS.
	\item ISIC: has explanatory notes too. 
	\item ISCO
\end{itemize}
